### 2019-11-09 Mathematical Statatistics/ch_02.rmd
ch2 work
ch2 work

```{r, c2_1a, echo = T}

@@

### 2.3

@@

```{r, c2_3, echo = T}

flights <- read.csv(paste0(data.dir, "FlightDelays.csv"),
                 header = T)

@@

>>>>

```{r echo = T}

log(mean(x)) == mean(xt)

@@

Does $m$ = $\tilde{m}$ ?

```{r echo = T}

log(median(x)) == median(xt)

### 2.2

Compute the median $\bar{x}$ and median of the eight numbers: 1, 2, 4, 5, 6, 8, 11, 15.

Let $f(x) = \sqrt{x}$

Apply the transformation, then compute the mean, $tilde{x}$ and median, m, of the transformed data.

```{r echo = T}

x <- c(1, 2, 4, 5, 6, 8, 11, 15)
xt <- sqrt(x)

+ Is $f(\bar{x}) = \tilde{x}$?

```{r echo = T}

sqrt(mean(x)) == mean(xt)

+ Is $f(m) = \tilde{m}$?

```{r echo = T}

sqrt(median(x)) == median(xt)

### 2.4

@@

```{r echo = T}

flights <- data.table(read.csv(paste0(data.dir, "FlightDelays.csv"),
                 header = T))

@@

a.) Create a table and bar chart of the departure times _(DepartTimes)_

```{r echo = T}

table(flights$DepartTime)

```{r echo = T, fig.height=3.5}

ggplot(flights, aes(DepartTime)) +
   geom_bar(aes(fill = ..count..)) +
   labs(title = "Depart Times")

\newpage

b.) Create a contingency table of the variables _Day_ and _Delay30_.

```{r echo = T}

delay <- table(flights$Day, flights$Delayed30)

pretty_kable(delay, "Flight Delays")

Show the proportions of delayed flights, by day:

```{r echo = T}

pretty_kable(round(prop.table(delay), 4) * 100, "Flight Delays Proportions")

\newpage

c.) Create side-by-side boxplots of the lengths of flight times, grouped by wether or not the flight was delayed at least 30 minutes:

```{r echo = T, fig.height=3.5}

ggplot(flights) +
   geom_boxplot(aes(Delayed30, FlightLength, fill = Delayed30)) +
   labs(title = "Flight Length by Delayed30")

d.) Do you think there is a relationship between the length of the flight and whether or not the departure time is delayed by at least 30 minutes?

The average flight time is the same, however, the flights that are delayed 30 minutes or more seem to be shorter overall.
